Global patterns of forest autotrophic carbon fluxes

### 2020-03-10 manuscript/manuscript draft.Rmd
misc

---
title: ""
author: ""
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [library.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}

@@

**Climate is a significant driver of FACF across broad spatial scales** [@luyssaert_co_2007; @cleveland_relationships_2011]([Hursh et al. 2017](https://onlinelibrary.wiley.com/doi/epdf/10.1111/gcb.13489)). The majority of studies have focused on exploring the relationships of FACF to mean annual temperature (MAT) and mean annual precipitation (MAP), as the most commonly reported site-level climate variables. These variables have the advantage that they describe broad trends in temperature and water availability, and therefore capture a lot of global-scale variation in climate. There is strong evidence that both MAT and MAP show significant positive relationships with FACF [@chu_does_2016]. However, as with latitude, the shape of those relationships is not always clear, and, again, is complicated by the use of different measures of FACF across studies. Various measures of primary productivity {**FACF?**} saturate at high levels of MAP, though the saturation points identified vary from 1500mm [@luyssaert_co_2007] up to 2445mm MAP [@schuur_productivity_2003]. Studies of the influence of MAT on productivity {**FACF?**} are less conclusive. Luyssaert et al. [-@luyssaert_co_2007] examined GPP and NPP and found that, while GPP increases linearly with MAT, NPP saturates at around 10$^\circ$C MAT. In contrast, Larjavaara and Muller-Landau [-@larjavaara_temperature_2012], find that increases in GPP saturate at approximately 25$^\circ$C MAT, while Schuur [-@schuur_productivity_2003] shows that NPP increases linearly with temperature. bbl:maybe remove following sentences The influence of these climate variables on productivity is further complicated by the possibility of interactive effects occurring between them. Taylor et al. [-@taylor_temperature_2017] showed that high rainfall had a negative effect on productivity where MAT was low, but a positive effect at sites with high MAT. Similarly, at sites with high MAT, increases in rainfall were found to enhance productivity, in contrast to cooler sites, where high levels of rainfall inhibit productivity.  {**It would be good to add some more citations on soil respiraiton. I'm sure BBL can help.**}

@@

Aannual wet days, cloud cover, and aridity were poor or non-significant explainers of variation in FACF, explaining less than 20% of the variation in each of the carbon fluxes (Figs. S4-S5; Table S2).

@@

>>>>

---
title: ""
author: ""
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [library.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \usepackage{setspace}\onehalfspacing
                  \usepackage{lineno}\linenumbers

@@

**Climate is a significant driver of FACF across broad spatial scales** [@luyssaert_co_2007; @cleveland_relationships_2011]([Hursh et al. 2017](https://onlinelibrary.wiley.com/doi/epdf/10.1111/gcb.13489)). The majority of studies have focused on exploring the relationships of FACF to mean annual temperature (MAT) and mean annual precipitation (MAP), as the most commonly reported site-level climate variables. These variables have the advantage that they describe broad trends in temperature and water availability, and therefore capture a lot of global-scale variation in climate. There is strong evidence that both MAT and MAP show significant positive relationships with FACF [@chu_does_2016]. However, as with latitude, the shape of those relationships is not always clear, and, again, is complicated by the use of different measures of FACF across studies. Various measures of primary productivity {**FACF?**} saturate at high levels of MAP, though the saturation points identified vary from 1500mm [@luyssaert_co_2007] up to 2445mm MAP [@schuur_productivity_2003]. Studies of the influence of MAT on productivity {**FACF?**} are less conclusive. Luyssaert et al. [-@luyssaert_co_2007] examined GPP and NPP and found that, while GPP increases linearly with MAT, NPP saturates at around 10$^\circ$C MAT. In contrast, Larjavaara and Muller-Landau [-@larjavaara_temperature_2012], find that increases in GPP saturate at approximately 25$^\circ$C MAT, while Schuur [-@schuur_productivity_2003] shows that NPP increases linearly with temperature. **bbl:maybe remove following sentences** The influence of these climate variables on productivity is further complicated by the possibility of interactive effects occurring between them. Taylor et al. [-@taylor_temperature_2017] showed a positive interaction between MAT and MAP in shaping tropical forest productivity, such that high rainfall had a negative effect on productivity in cooler climates, compared to a positive effect in warmer climates. {**It would be good to add some more citations on soil respiraiton. I'm sure BBL can help.**}

@@

Annual wet days, cloud cover, and aridity were poor or non-significant explainers of variation in FACF, explaining less than 20% of the variation in each of the carbon fluxes (Figs. S4-S5; Table S2).

@@

## misc content for discussion
- the observed positive interaction between MAT and MAP for $ANPP_woody$ is consitent with the @taylor_temperature_2017 analysis showing such an interaction for $ANPP$ in tropical forests. Similar to their analysis, we find a cross-over point at ~20C. However, we don't find such an interaction for $ANPP$, and we show a contrasting negative interaction for $NPP$. Some of this is may be stochasitic/ driven by composition of the dataset, and the interactions we observe are not internally consistent.

- consistent with [Hofhansl et al. 2015](https://agupubs.onlinelibrary.wiley.com/doi/full/10.1002/2014GB004934) (**verify**) , we found a slight tendency for warmer sites to have higher aboveground allocation

-results are consistent with *Muller-Landau et al., in review*
